### 2020-10-26 thesis/__latexindent_temp.tex
Update index

\chapter{Digital Customer Self-Service (DCSS)}

@@

\chapter{Governmental Regulations}

@@

\section{DSGVO}

\section{DVG}

\chapter{DCSS Providers}

@@

\section{Description}

\section{CSS Solutions}

\chapter{DCSS Scenarios}

@@

\subsection{Unemployment Benefit (AG2)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Training Promotion (BAföG)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Drivers License}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\subsection{Company Registration and Approval}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\subsection{Visa Issuance}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
\end{itemize}

\section{DSGVO}

The DSGVO influences DCSS by regulating how digitally collected personal information (which is common in DCSS) has to be managed. This means, DCSS providers have to 
keep this regulation in mind when designing their solutions. It has implications on integration in that DSGVO compliance requires special management of data, 
which an integration system has to make possible (DCSS providers use it).

It has to be analyzed in regard to:
\begin{enumerate}
     \item Which parts of the regulation describe requirements for features of DCSS providers
     \item Which parts of the regulation describe requirements for integrations
\end{enumerate}

\subsection{Transparent Accessability}
The enterprise or organization can have the duty to make information about personal data accessible in transparent and understandable ways

\subsection{Deletion of Personal Data}
The user can have the right of removal of personal data

\subsection{Correction of Personal Data}
The user can have the right of modification of personal data.

\subsection{Information about collected Personal Data}
The user can have the right to be informed about various information of collected and stored personal data such as usage, duration of storage, ...

\subsection{Restriction of Processing}
The user can have the right to restrict the way in which personal data is processed

\subsection{Availability of Transferral of Personal Data}
The user can have the right to transfer personal data to himself or separate entities (company, organization).

\section{DVG}

\subsection{e-Prescription}
Reference can be found in the "rzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz fï¿½r mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}

\section{PSD2}

The regulation is about how digital payment self-service providers have to function. This includes their communication / integration\cite{psd2Summary}.
\\\\
Full law at \cite{psd2}
\\\\
Regulation: "Payment Services Directive 2" (PSD2) (European law)
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Payments and transfers. Self-service: Payment services are DCSS providers and offer digital execution of payments and transfers
\end{itemize}
~\\
The regulation has to be analyzed regarding:
\begin{enumerate}
     \item Which parts of the regulation describe required features of the self-service provider
     \item Which parts of the regulation describe requirements for integration
\end{enumerate}

\section{Requirements}

\chapter{Enterprise Architectures}

\section{Modeling of the real world}

\section{Modeling Challenges}

\section{Enterprise Architecture Patterns (EAP)}

\chapter{Relevant Systems and Data}

@@

\section{EAPs}

\section{Architecture Bricks}

\section{Data Bricks}

\section{Integration Requirements}

\subsection{Regarding Integration Architecture}

\subsection{Regarding Business Connector}

\chapter{Integration}

\section{Definition}

\section{Requirements}

\subsection{Loose Coupling}

\subsection{Homogeneous Landscapes}

\section{Enterprise Integration Patterns (EIP)}

\subsection{Pattern 1}

\subsection{Pattern 2}

\chapter{Business Connector}

@@

\section{Functionalities and Interfaces}

\section{Integration Requirements}

\subsection{Regarding Enterprise Architecture}

\subsection{Regarding Integration Architecture}

\section{Documentation}

\subsection{Connector as Architecture Brick}

>>>>

\chapter{Basis}

\section{Digital Customer Self-Service (DCSS)}

@@

@@

\section{DCSS Provider}

@@

\subsection{Description}

\subsection{CSS Solutions}

\subsection{Business Connector}

\section{Enterprise Architecture}

\subsection{Modeling of the real world}

\subsection{Modeling Challenges}

\subsection{Enterprise Architecture Patterns (EAP)}

\section{Integration}

\subsection{Definition}

\subsection{Requirements}

\subsubsection{Loose Coupling}

\subsubsection{Homogeneous Landscapes}

\chapter{Preparatory Work}

\section{OZG Scenarios}

@@

\begin{itemize}
     \item Unemployment Benefit (AG2)
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\item Training Promotion (BAföG)
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\item Drivers License
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Process Diagram of Application
     \item Click-Dummy
\end{itemize}

\item Company Registration and Approval
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

\item Visa Issuance
\begin{itemize}
     \item Data Schema
     \item Process Diagram
\end{itemize}

\end{itemize}

\section{Relevant Systems and Data}

@@

\subsection{EAPs}

\subsection{Architecture Bricks}

\subsection{Data Bricks}

\subsection{Integration Requirements}

\subsubsection{Regarding Integration Architecture}

\subsubsection{Regarding Business Connector}

@@

\subsection{Functionalities and Interfaces}

\subsection{Integration Requirements}

\subsubsection{Regarding Enterprise Architecture}

\subsubsection{Regarding Integration Architecture}

\subsection{Documentation}

\subsubsection{Connector as Architecture Brick}
